Imputation of Incomplete Multilevel Data with \pkg{mice}

### 2021-10-11 Multilevel Missing Data/Multilevel Missing Data.Rmd
Translate outline

-	Waarom zijn standaard (ad hoc) methoden niet geschikt?

-	Wat is heterogeniteit? (i.e. variability binnen studies vs. variability tussen studies). Random effects voor intercept term, predictor effects, en/of variance residual error

-	JOMO aanpak (misschien buiten beschouwing laten?)

-	MICE aanpak: one-stage imputation versus two-stage imputation methods

-	Imputatie van studie-level versus patient-level covariates

-	Omgaan met MNAR

>>>>

-	Why are standard (ad hoc) methods not well suited?

-	What is heterogeniety? (i.e. variability within studies vs. variability between studies). Random effects for intercept term, predictor effects, and/or variance residual error

- Systematic vs sporadic missingness

-	MICE approach: one-stage imputation versus two-stage imputation methods

-	Imputation of study level versus patient-level covariates

-	Handling MNAR

- Case study: metamisc::impact()

# Think about adding

- JOMO in mice
